---
title: "Jian Shen's CV"
author: Jian Shen
date: "`r Sys.Date()`"
params:
  pdf_mode:
    value: false
  cache_data:
    value: false
output:
  pagedown::html_resume:
    css: ['css/cv.css', 'css/custom.css','resume']
    self_contained: true
---


```{r, include=FALSE}
knitr::opts_chunk$set(
  results='asis', 
  echo = FALSE
)

library(magrittr) # For the pipe
source("cv_printing_functions.r")

# Read in all data and initialize a CV printer object
CV <- create_CV_object(
  data_location = "https://docs.google.com/spreadsheets/d/1HERsY82vxw9x2EcnnsojCfUv5uIiK_UJHK3Do2NbPsQ/edit#gid=917338460",
  pdf_mode = params$pdf_mode,
  cache_data = params$cache_data
)

CV$entries_data <- CV$entries_data %>% dplyr::filter(in_resume_long == TRUE)
```


```{r}
# When in pdf export mode the little dots are unaligned, so fix that with some conditional CSS.
if(params$pdf_mode) {
    cat("
<style>
:root{
  --decorator-outer-offset-left: -6.5px;
}
</style>")
}
```


Aside
================================================================================


```{r}
if(params$pdf_mode){
  cat("View this CV online with links at _xxxxxx/cv/_")
} else {
  cat("[<i class='fas fa-download'></i> Download the latest version ](https://github.com/shenjianwhy/cv/jianSHEN_cv.pdf)")
}
```

Software {#software}
--------------------------------------------------------------------------------

- <i class="fas fa-box-open"></i> [Package {aeda}](https://github.com/ShenJianWHy/Exploratory-Data-Analysis) - Author. 


Contact {#contact}
--------------------------------------------------------------------------------


```{r}
CV %>% print_contact_info()
```

Certificates {#certificates}
--------------------------------------------------------------------------------

- <i class="fas fa-file-contract"></i> [Certified International Investment Analyst (CIIA)](https://www.aciia.org/) 

- <i class="fas fa-file-contract"></i> Associate of China Actuaries Association (ACAA)

- <i class="fas fa-file-contract"></i> CFA Level III candidate


Skills {#skills}
--------------------------------------------------------------------------------

- **Highly skilled in:** Python, R, R shiny, SQL, VBA, Tableau, Excel

- **Intermediate level:** Talend, html, Git, LaTeX

- **Experienced in:** data analysis and visualization, statistical learning, and optimization methods

Languages {#languages}
--------------------------------------------------------------------------------

- **Chinese:** Native

- **English:** Proficient

- **French:** Beginner


Main
================================================================================

Jian Shen {#title}
--------------------------------------------------------------------------------

```{r}
# Note the special double pipe so we modify the CV object in place
CV %<>% print_text_block("intro") 
```

Education {data-icon=graduation-cap data-concise=true}
--------------------------------------------------------------------------------

```{r}
CV %<>% print_section('education')
```

Industry Experience {data-icon=suitcase}
--------------------------------------------------------------------------------

```{r}
CV %<>% print_section('industry_positions')
```


Research and Projects {data-icon=share-alt}
--------------------------------------------------------------------------------


```{r}
CV %<>% print_section('projects')
```


Disclaimer {#disclaimer style="width: var(--sidebar-width); padding-left: var(--sidebar-horizontal-padding);"}
--------------------------------------------------------------------------------

Code available on <i class="fa fa-github"></i>  [GitHub](https://github.com/shenjianwhy/cv)


Last updated on `r Sys.Date()`
